Ethereum: Un registre de transactions généraliste, sécurisé et décentralisé\\ {\smaller \textbf{révision Homestead}}

### 2016-10-23 Paper.tex
mise à jour

\section{Transaction Execution} \label{ch:transactions}

The execution of a transaction is the most complex part of the Ethereum protocol: it defines the state transition function $\Upsilon$. It is assumed that any transactions executed first pass the initial tests of intrinsic validity. These include:

>>>>

\section{Exécution de la transaction} \label{ch:transactions}

L'exécution d'une transaction est la partie la plus complexe du protocole Ethereum: elle définit la fonction de transition d'état $\Upsilon$. It is assumed that any transactions executed first pass the initial tests of intrinsic validity. These include:
